\documentclass{report}
\usepackage[english]{babel}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{amssymb}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{float}
\usepackage{listings}
\usepackage{color}

\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\graphicspath{{images/}}

\title{Playing with 3D equations and planes/graphs}

\author{Mr Ashlin Darius Govindasamy\\ \large{University of South Africa}}

\date{\today}

\begin{document}
\maketitle
\newpage

\tableofcontents

%for adding page numbers
\pagenumbering{arabic} 

\chapter*{Introduction}
\input{chapters/introduction.tex}

\chapter{Graphing lines and equations in 3D space using software}
Why graph in 3D? In school or universities, they don't make you draw the 3D graph or teach you that (that's because during examinations you use just pen and paper and methodology to solve the problem with no access to the computer). But in real life, you can use the computer to draw a 3D graph in seconds to give you a picture of your function.

When playing or calculating with functions I would like to see what that function is doing in 3D. This is a good way to see what the function is doing in 3D. For example, finding a plane in 3D perpendicular to a point in 3D space or another 3D plane. The way universities tell you to check if your equations are correct is to prove them mathematically using some concrete methodology or theorem. This is a good way to prove your equations are correct.
I believe that a much easier way to prove your equations is to graph them in 3D and it looks cooler to visualize them it also gives you a better idea/understanding of what the function is doing in 3D.

So when I am going to explain the 3D planes in the next chapter I will use the following software to graph the 3D planes to give you a picture of what is happening. For now, I'm going to explain free software graphing methodologies so you can plot any 3D functions.

\input{chapters/software.tex}

\chapter{Lines and Planes in 3-Space}
\input{chapters/lines_in_3d_space.tex}

\newpage

\end{document}
